\documentclass[11pt,a4paper,roman]{moderncv}        % possible options include font size ('10pt', '11pt' and '12pt'), paper size ('a4paper', 'letterpaper', 'a5paper', 'legalpaper', 'executivepaper' and 'landscape') and font family ('sans' and 'roman')



\moderncvstyle{banking}                            % style options are 'casual' (default), 'classic', 'oldstyle' and 'banking'oldstyle
\moderncvcolor{blue}                              % color options 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'
% \renewcommand{\familydefault}{\fourier}         % to set the default font; use '\sfdefault' for the default sans serif font, '\rmdefault' for the default roman one, or any tex font name
\nopagenumbers{}                                  % uncomment to suppress automatic page numbering for CVs longer than one page

\usepackage[T1]{fontenc}
\usepackage{charter}
\usepackage[dvipsnames]{xcolor}
\color{green}
\usepackage[UKenglish]{babel}% http://ctan.org/pkg/babel
% \usepackage[UKenglish]{isodate}% http://ctan.org/pkg/isodate

% character encoding
\usepackage[utf8]{inputenc}                       % if you are not using xelatex ou lualatex, replace by the encoding you are using
\usepackage{CJKutf8}                              % if you need to use CJK to typeset your resume in Chinese, Japanese or Korean

\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,      
    urlcolor=cyan,
}

\urlstyle{same}


% adjust the page margins
\usepackage[scale=0.75]{geometry}

% personal data
\name{Hendry}{Khoza}
% \signature{Khoza SH}
\title{Application for MICT Intership}                               % optional, remove / comment the line if not wanted
\address{26 Frangipani St}{Pretoria}% optional, remove / comment the line if not wanted; the "postcode city" and and "country" arguments can be omitted or provided empty
\phone[mobile]{+27 81-249-0306}                   % optional, remove / comment the line if not wanted
\email{h3khoza@gmail.com}                               % optional, remove / comment the line if not wanted
\homepage{www.hendry.xyz}                         % optional, remove / comment the line if not wanted

\begin{document}
%-----       letter       ---------------------------------------------------------
% recipient data

\recipient{Capitec Bank Ltd}{Stellenbosch, Western Cape, ZA}
\date{\today}
\opening{Dear sir/madam}
\closing{Yours sincerely,}
% \enclosure[Adjunto]{CV}          % use an optional argument to use a string other than "Enclosure", or redefine \enclname

\makelettertitle

I so pleased to be applying for the analyst developer front-end position at Capitec. One of the reasons why I am so happy about this opportunity is how passionate I am with system development methodology, special Dev-Ops.
For further references see \href{http://www.sharelatex.com}{Something 
Linky} or go to the next url: \url{http://www.sharelatex.com} or open 
the next file \href{run:./file.txt}{File.txt}

{\fontfamily{lmr}\selectfont
This text uses a different font typeface
Over my career, I have learned many skills but one that sticks among all is the skill to work with a team to create an amazing product. Sharing Knowledge with others and see them use that knowledge in a way I’ve never thought to, brings joy to me. You will be making a great choice choosing me for this role because:
}


\vspace{0.5cm}

\begin{itemize} \itemsep 1em 
	\item Not only do I know the fundamental of database management and query language such as SQL but I possess real world I implementation of database design using oracle database and NET(C\#) framework
  
	\item I have experience building android applications and one of the prerequisites to build android applications is to know XAML. I believe these skills will be of great use at Capitec.


	\item When I was at university, I built a website for clients. Most of my clients complimented me on how easy it is now to find their website on search engines. All this is due to my ability to optimize the website, specifically search engines optimization.

	\item My academics demonstrate very well how my knowledge of object-oriented programming. From working with C++ at university and learning Java to develop android applications. I have grabs the method of developing software while having objects oriented in mind.
\end{itemize}

If so far I have convinced you to consider me for this position, I would be pleased to hear from you as soon you go through my document


\vspace{0.5cm}


\makeletterclosing

\end{document}

