%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 2.0 (8/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Thanks : Rishi Shah 's Contribution
% inspired by his awesome contribution:
% https://www.overleaf.com/articles/rishi-shahs-resume/vgxvkmxktyxn
% Author : Allianzcortex
% contact me : github.com/Allianzcortex
% email : iamwanghz#gmail.com
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.40in,top=0.3in,right=0.75in,bottom=0.1in]{geometry} % Document margins
\usepackage{fontawesome}
\usepackage{times}
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}}
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{Hendry Khoza} % Your name 


% \usepackage[hidelinks]{hyperref}

\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,      
    urlcolor=blue,
}

\urlstyle{same}


\newlength{\spacebox}
\settowidth{\spacebox}{8888888888888888888}			% Box to align text
\newcommand{\sepspace}{\vspace*{1em}}           % Vertical space macro

\newcommand{\EducationEntry}[4]{
        \noindent \textbf{#1} \hfill \textit{#2} \\     % Study
        \noindent \textit{#3} \\        % School
        \noindent  #4  % Description
        \normalsize \par}


\newcommand{\WorkEntry}[4]{				  % Same as \EducationEntry
        \noindent \textbf{#1} \hfill \textit{#2} \\      % Jobname
        \noindent \textit{#3} \\              % Company
        \noindent\hangindent=2em\hangafter=0  #4 % Description
        \normalsize \par}


\newcommand{\ProjectsEntry}[8]{				  % Same as \EducationEntry
		\noindent \textbf{#1} \hfill \\     % Jobname
    \noindent \textit{#2} | \textit{#3} \\              % Company
    \noindent\hangindent=2em\hangafter=0  #4 \\ % Description
    \noindent \small #5 | #6 | #7 | #8              % Company
		\normalsize \par}

\newcommand{\SkillsEntry}[2]{      % Same as \PersonalEntry
		\noindent\hangindent=2em\hangafter=0 % Indentation
		\parbox{\spacebox}{        % Box to align text
    \textit{\textbf{#1}}}			   % Entry name (birth, address, etc.)
		\hspace{1em} #2 \par}    % Entry value	


\address{\faGithub{ \url{www.github.com/hendry3k} } \faLink{ \url{www.hendry.xyz} } \faEnvelope{ \url{h3khoza@gmail.com}}}
\address{\faMapMarker{ 26 Frangipani St, Pretoria } \faPhone{ (+27) 81-249-0306}} % Your address

\begin{document}

%----------------------------------------------------------------------------------------
%	OBJECTIVE SECTION
%----------------------------------------------------------------------------------------
\begin{rSection}{Objective}
{Computer Engineer with programming experience in web development, seeking 12 months internship  for software development roles.}
\end{rSection}

% \sepspace
%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------
\begin{rSection}{Education}
        \EducationEntry{Computer Systems Engineering}{2018-Present}
        {\href{https://www.tut.ac.za/} {Tshwane University of Technology}}
        {I have an average pass mark of 65 percent including a distinction in technical programming using the C++ language. I majored in mathematics and systems  development. I pass communication skills and writing skills with 70 percent}
        % \sepspace

        \EducationEntry{Matric (Grade 12)}{2009-2013}
        {\href{https://sincobilesecondaryschool.co.za/}{Sincobile Secondary School}}
        {I was one of the top achievers in my class. I have a distinction in mathematics and level 6 in life science and physical science. I participated in the school soccer term and school debate.}
        % \sepspace
\end{rSection}

% \sepspace
%--------------------------------------------------------------------------------
%    Projects And Seminars
%-----------------------------------------------------------------------------------------------
\begin{rSection}{Projects}
        \ProjectsEntry{Radserve (A website for a client)}
        {\faGithub{ \url{https://github.com/hendry3k} } }{\faLink{ \url{https://www.radserve.co.za} }}
        {I developed this website for a client that was looking to make sure that his business is available online. The website is well designed and responsive, also contains a working contact form using Formspree API}
        {\{JavaScript}{React}{CSS-in-JS}{HTML\}}
        % \sepspace
   
        \ProjectsEntry{Safe System using shape recognition}
        {\faGithub{ \url{https://github.com/hendry3k} } }{}
        {The system uses shape recognition as a second method of authentication to gain access to the system. A random shape is generated and sent to the user, the user must scan the sent shape to gain access to the system.}
        {\{Python}{OpenCV}{Raspberry Pi}{Tkinter\}}
        % \sepspace

        \ProjectsEntry{Online Cellphone store}
        {\faGithub{ \url{https://github.com/hendry3k/cell-phone-store} } }{\faLink{ \url{https://cell-phone-store.netlify.app/} }}
        { An e-commerce website that sells second-hand cellphone. The website is built with react and the data is provided on the fly with react context API}
        {\{JavaScript}{React}{CSS}{HTML\}}
        % \sepspace
           
        \ProjectsEntry{Bankist (Minimalist Marketing Website)}
        {\faGithub{ \url{https://github.com/hendry3k/bankist} } }{\faLink{ \url{https://hendry.xyz/bankist/} }}
        {A one-page marketing website for a fictional bank. The website has modern features such as auto-scroll to section, Lazy loading Images, carousel or slider, and more.  All the features are built from scratch.}
        {\{JavaScript}{HTML}{CSS}{\}}
        % \sepspace

\end{rSection}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------
\begin{rSection}{Work Experience}
        \WorkEntry{Student Assistant}{2020-2021}
        {\href{https://www.tut.ac.za/} {Tshwane University of Technology}, Full-time}
        {My Responsibility was to assist students where they find difficulties in their studies, particularly in mathematics and programming. I was also responsible to open las where a student can come to practice.}
        % \sepspace

        \WorkEntry{Web Developer}{2017-2018}
        {\href{https://www.hscom.co.za/} {HSCOM inc}, Part-time}
        {I designed and developed websites for clients. I improved the existing clients’ websites for better results on the search engines. I was also a call consultant for clients who are having technical.}

        % \EducationEntry{Participate of MTN Bussiness App of the year}{Sept... - 2020}
        % {\href{https://www.appoftheyear.co.za/} {\color{blue}MTN App of the Year}, Full-time}
        % {I was responsible to assist students where they find difficulties in their studies. I also helped to maintain labs where students can practice and do their assignments}
        % % \sepspace

\end{rSection}

\pagebreak

%--------------------------------------------------------------------------------
%     Technical Skills
%-----------------------------------------------------------------------------------------------
\begin{rSection}{Technical Skills}



\SkillsEntry{Programming}{  Runners up in B.G.Shirke Vidyarthi Competition for Innovative Project organized by Pune Construction Engineering Research Foundation in January 2018 \& C++, Python, Java, Go}
% \SkillsEntry{}{}
\SkillsEntry{Web Development}{HTML5, CSS3, JavaScript, React}
% \SkillsEntry{}{}
\SkillsEntry{DBMS}{MySQL, Oracle, MongosDB}
% \SkillsEntry{}{}
\SkillsEntry{Software}{\textsc{Android Studio}, \LaTeX, \textsc{Linux}}
% \SkillsEntry{}{}
\SkillsEntry{Strengths}{Oral and Written Communication}
\SkillsEntry{}{Reliable and Consistent}
\SkillsEntry{}{Committed to Lifelong Learning}
\SkillsEntry{}{Team Building}


        \begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
        Programming: \ & aaa,bbb,ccc,ddd,eee,fff,ggg,hhh \\
        Software \& Tools: & {\textbf{Backend: }}qqqq,wwww,eeee,rrrr,tttt,yyyy,uuuu,iiii\\
        & {\textbf{FrontEnd: }}aaaaa,bbbbb,eeee,cccc\\
        & {\textbf{Others: }}uuuu,uyyy,oooo,aaaa,vvv,eeee
        \end{tabular}
\end{rSection}

%----------------------------------------------------------------------------------------
%	TECHNICAL STRENGTHS SECTION
%----------------------------------------------------------------------------------------



{\bf Work Station1,Strange Place } \hfill {\em May 2002 - June 2004} 
{\textit{Backend Developer}}\\
- Someone I know recently combined Maple Syrup  buttered Popcorn thinking it would taste like caramel popcorn. It didn’t and they don’t recommend anyone else do it either.
\\- Should we start class now, or should we wait for everyone to get here.Lets all be unique together until we realise we are all the same.

{\bf Work Station2,Strange Place2} \hfill {\em June 2005 - April 2008} 
\\{\textit{Full-Stack Engineer}}
\\- Someone I know recently combined Maple Syrup buttered Popcorn thinking it would taste like caramel popcorn. It didn’t and they don’t recommend anyone else do it either.
\\- Should we start class now, or should we wait for everyone to get here.Lets all be unique together until we realise we are all the same.

% \\- xx
% \\- xx
% there should be more lines

%Minor in Linguistics \smallskip \\
%Member of Eta Kappa Nu \\
%Member of Upsilon Pi Epsilon \\


\begin{rSection}{Award}
- First Prize\\
- Second Prize\\
- Third Prize\\
\end{rSection}

%	EXAMPLE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Academic Achievements} 
 Runners up in B.G.Shirke Vidyarthi Competition for Innovative Project organized by Pune Construction Engineering Research Foundation in January 2018
\item Won First Prize in Model Making Competition Organized by Symbiosis Institute of Technology, Pune.
\end{rSection}

% \newpage

%----------------------------------------------------------------------------------------
% Extra Curricular
%----------------------------------------------------------------------------------------

\begin{rSection}{Extra-Cirrucular} \itemsep -3pt
\item Co-Organized “ Nirmitee 2017” - a National Symposium of Civil Department of MIT, Pune
\item Attended a workshop on Autodesk Revit at IIT Bombay in 2014.
\item Winner of Inter Departmental Football Competition 2015.
\item Member of the  Rotaract Club Of Pune Pride from 2014 to 2017.
\item Worked for a start-up company Named OUST as a Regional Marketing Manager
\item Trained and disciplined in National Cadet Corps (NCC), IIT Kanpur for a year.
 \item  Participated in Vijyoshi Camp 2012 organized at Indian Institute of Science, Bangalore.
 \item Won 2nd position in Kho-Kho in Intramurals conducted by Physical Education Section, IIT Kanpur.
 \item Pursued French as second language during secondary school from Grade 6 to Grade 10. Also participated in French Song Competition and French G.K. Quiz in Class 10th. %

\end{rSection}

\begin{rSection}{Personal Traits}
\item Highly motivated and eager to learn new things.
\item Strong motivational and leadership skills.
\item Ability to work as an individual as well as in group.
\end{rSection}
\end{document}
