\documentclass[11pt,a4paper,roman]{moderncv}        % possible options include font size ('10pt', '11pt' and '12pt'), paper size ('a4paper', 'letterpaper', 'a5paper', 'legalpaper', 'executivepaper' and 'landscape') and font family ('sans' and 'roman')

\mderncvstyle{banking}                            % style options are 'casual' (default), 'classic', 'oldstyle' and 'banking'oldstyle
\moderncvcolor{blue}                              % color options 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'
% \renewcommand{\familydefault}{\fourier}         % to set the default font; use '\sfdefault' for the default sans serif font, '\rmdefault' for the default roman one, or any tex font name
\nopagenumbers{}                                  % uncomment to suppress automatic page numbering for CVs longer than one page

\usepackage[T1]{fontenc}
\usepackage{charter}

% character encoding
\usepackage[utf8]{inputenc}                       % if you are not using xelatex ou lualatex, replace by the encoding you are using
\usepackage{CJKutf8}                              % if you need to use CJK to typeset your resume in Chinese, Japanese or Korean

% \usepackage[ulrcolor=cyan]{hyperref}

% \hypersetup{
%     colorlinks=true,
%     linkcolor=blue,
%     filecolor=magenta,      
%     urlcolor=cyan,
% }

% \urlstyle{same}


% adjust the page margins
\usepackage[scale=0.75]{geometry}

% personal data
\name{Hendry}{Khoza}
% \signature{Khoza SH}
\title{Smart My Company Internship program}                               % optional, remove / comment the line if not wanted
\address{26 Frangipani St}{Pretoria}% optional, remove / comment the line if not wanted; the "postcode city" and and "country" arguments can be omitted or provided empty
\phone[mobile]{+27 81-249-0306}                   % optional, remove / comment the line if not wanted
\email{h3khoza@gmail.com}                               % optional, remove / comment the line if not wanted
\homepage{www.hendry.xyz}                         % optional, remove / comment the line if not wanted

\begin{document}

\recipient{Smart My Company}{509 Cliff Ave, Waterkloof Ridge}
\date{\today}
\opening{Dear Hiring team}
\closing{Yours sincerely,}
% \enclosure[Adjunto]{CV}          % use an optional argument to use a string other than "Enclosure", or redefine \enclname

\makelettertitle

I am so thrilled to be applying for the Smart My Company internship program. I 
am writing this letter to express facts about myself that my resume simply cannot
highlight. That I have a passion for system development. I have been teaching 
myself what I can while studying computer system engineering at Tshwane university
of technology. JavaScript was such a wonderful coding language for me, being able to use one programing language to build an entire web application is such amazing, not to even mention that you can build desktop applications with javaScript

When I was at university I took multiple Udemy courses to supplement my school
syllabus. Which are \href{https://www.udemy.com/course/advanced-css-and-sass/}{\color{cyan} advanced CSS}, 
\href{https://www.udemy.com/course/the-complete-javascript-course/learn/}{\color{cyan}Complete JavaScript}, and Node JS all by
\href{https://twitter.com/jonasschmedtman}{\color{cyan}Jonas Schmedtmann}. I feel in love with web technology ever since, from working
with React, Express brings joy to me.


I am good at programming, I didn't limit myself to one programing language that 
was thought in my class which is c++,  I took extra time to learn multiple 
programming languages such as Python, Go, and typescript. Now I am in the process of
learning rust. I have a good grasp of working with modern tools such as Git and
cloud computing. My favorite tool is the bash scripting language because it
allows me to automate a lot of my work


I know that with the opportunity to fully invest myself in this career I would
be able to become a great software developer in your team.


\vspace{0.5cm}


\makeletterclosing

\end{document}

