\documentclass[11pt,a4paper,roman]{moderncv}        % possible options include font size ('10pt', '11pt' and '12pt'), paper size ('a4paper', 'letterpaper', 'a5paper', 'legalpaper', 'executivepaper' and 'landscape') and font family ('sans' and 'roman')


\moderncvstyle{classic}                            % style options are 'casual' (default), 'classic', 'oldstyle' and 'banking'
\moderncvcolor{green}                              % color options 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'
\renewcommand{\familydefault}{\sfdefault}         % to set the default font; use '\sfdefault' for the default sans serif font, '\rmdefault' for the default roman one, or any tex font name
\nopagenumbers{}                                  % uncomment to suppress automatic page numbering for CVs longer than one page

% character encoding
\usepackage[utf8]{inputenc}                       % if you are not using xelatex ou lualatex, replace by the encoding you are using
\usepackage{CJKutf8}                              % if you need to use CJK to typeset your resume in Chinese, Japanese or Korean


% adjust the page margins
\usepackage[scale=0.75]{geometry}

% personal data
\name{Hendry}{Khoza}
% \signature{Khoza SH}
% \title{Application for MICT Intership}                               % optional, remove / comment the line if not wanted
\address{26 Frangipani St}{Pretoria}% optional, remove / comment the line if not wanted; the "postcode city" and and "country" arguments can be omitted or provided empty
\phone[mobile]{+27 81-249-0306}                   % optional, remove / comment the line if not wanted
\email{h3khoza@gmail.com}                               % optional, remove / comment the line if not wanted
\homepage{www.hendry.xyz}                         % optional, remove / comment the line if not wanted

\begin{document}
%-----       letter       ---------------------------------------------------------
% recipient data
\recipient{Ubuntu Institute}{164 Katherine Street}
\date{\today}
\opening{Dear sir/madam}
\closing{Yours sincerely,}
% \enclosure[Adjunto]{CV}          % use an optional argument to use a string other than "Enclosure", or redefine \enclname

\makelettertitle

I am so excited to be applying for the MICT internship at ubuntu Institute.
Over the years I was at university, I focused on learning skills that would
make me a better south African and be able to tackle the problem that we face
now such as poverty, racism, and unemployment


I believe I am the best fit for this internship because:
\begin{itemize} \itemsep1em 
	\item When I was at University I manage to start my own business developing websites for clients. This experience thought me a lot about entrepreneurship
  
	\item I manage to teach myself more than what was thought in my courses such as python programming and web development

	\item I remember when I wrote my first Hello world program It felt like I was part of the minority of people who can code in this world. My goal as a programmer was to create games. I've never got to reach my goal but trying to pursue this goal created a passion in me about writing computer programs. I've contributed to open-source projects and built my own portfolio website.

	\item I have great communication and writing skills, Most of which I learn when I was a student assistant, helping students with mathematics
\end{itemize}

For the above reasons, I hope I have convinced you to choose me for this position. If so would love to hear from you.


\vspace{0.5cm}


\makeletterclosing

\end{document}

