\documentclass[11pt,a4paper,roman]{moderncv}        % possible options include font size ('10pt', '11pt' and '12pt'), paper size ('a4paper', 'letterpaper', 'a5paper', 'legalpaper', 'executivepaper' and 'landscape') and font family ('sans' and 'roman')

\moderncvstyle{banking}                            % style options are 'casual' (default), 'classic', 'oldstyle' and 'banking'oldstyle
\moderncvcolor{blue}                              % color options 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'
% \renewcommand{\familydefault}{\fourier}         % to set the default font; use '\sfdefault' for the default sans serif font, '\rmdefault' for the default roman one, or any tex font name
\nopagenumbers{}                                  % uncomment to suppress automatic page numbering for CVs longer than one page

\usepackage[T1]{fontenc}
\usepackage{charter}

% character encoding
\usepackage[utf8]{inputenc}                       % if you are not using xelatex ou lualatex, replace by the encoding you are using
\usepackage{CJKutf8}                              % if you need to use CJK to typeset your resume in Chinese, Japanese or Korean

% \usepackage[ulrcolor=cyan]{hyperref}

% \hypersetup{
%     colorlinks=true,
%     linkcolor=blue,
%     filecolor=magenta,      
%     urlcolor=cyan,
% }

% \urlstyle{same}


% adjust the page margins
% \usepackage[scale=0.75]{geometry}
\usepackage[scale=0.75, top=2.5em, right=7em, bottom=1em, left=5em]{geometry}

% personal data
\name{Hendry}{Khoza}
% \signature{Khoza SH}
\title{University Placement Program}                               % optional, remove / comment the line if not wanted
\address{26 Frangipani St}{Pretoria}% optional, remove / comment the line if not wanted; the "postcode city" and and "country" arguments can be omitted or provided empty
\phone[mobile]{+27 81-249-0306}                   % optional, remove / comment the line if not wanted
\email{h3khoza@gmail.com}                               % optional, remove / comment the line if not wanted
\homepage{www.hendry.xyz}                         % optional, remove / comment the line if not wanted

\begin{document}

\recipient{Gijima} {P O Box 10629 \\ Centurion \\ 0046}
\date{\today}

\makeatletter
\renewcommand*{\makeletterclosing}{
  \@closing\\% <===================================================
  {\bfseries\@firstname~\@lastname}%
  \ifthenelse{\isundefined{\@enclosure}}{}{%
    \\%
    \vfil%
    {\color{color2}\itshape\enclname: \@enclosure}}%
    \vfil}
\makeatother


\opening{Dear Hiring team}

\closing{Yours sincerely,}
% \enclosure[Adjunto]{CV}          % use an optional argument to use a string other than "Enclosure", or redefine \enclname

\makelettertitle

This letter is to express my interest in the University placement program with
Gijima. With all of my skills and knowledge, I know I will be a valuable member
of your team.

I am a young, highly motivated computer system student at the Tshwane
University of Technology with a strong ability to understand programming
concepts, write computer programs while being consistent with a team. I have
studied computer System Engineering for two years, and I have completed all 24
modules with an average pass mark of 60%. In my years of being a student at the
Tshwane University of Technology, I have maintained a reputation of being
extremely efficient and professional in my work. I am fluent with programming
tools, notable with visual studio, Git, Docker, Qt Creator, and more. In
addition to Git, I have thought it myself it wasn't part of my academic
syllabus.

I am currently a freelancer, Developing software for clients. The number of
clients I receive keep growing, while the feedback I get is overwhelmingly
positive. I have developed a website for a client that sells and repairs
medical equipment, With a marketing website's target audience being online. I
have made the website to be visually beautiful while getting the point across.
I am familiar with making a tight deadline, because of this, my client
appreciates working with me.  In my free time, I enjoy building side projects
and learning a new programming language.

With Gijima being one of the most exciting IT companies in South Africa, I have
a strong desire to contribute my skills to ensure that Gijima is visually on
top of its game. I am hungry for a challenge, and I believe Gijima is the
perfect place for me to grow even more as a Software Engineer and put my
knowledge and skills to their proper use.

Thank you for considering me for the  University Placement Program within your
company. I look forward to meeting you. Please do not hesitate to contact me if
you have any questions.


\makeletterclosing

\end{document}

