\documentclass[11pt,a4paper,roman]{moderncv}        % possible options include font size ('10pt', '11pt' and '12pt'), paper size ('a4paper', 'letterpaper', 'a5paper', 'legalpaper', 'executivepaper' and 'landscape') and font family ('sans' and 'roman')

\moderncvstyle{banking}                            % style options are 'casual' (default), 'classic', 'oldstyle' and 'banking'oldstyle
\moderncvcolor{blue}                              % color options 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'
% \renewcommand{\familydefault}{\fourier}         % to set the default font; use '\sfdefault' for the default sans serif font, '\rmdefault' for the default roman one, or any tex font name
\nopagenumbers{}                                  % uncomment to suppress automatic page numbering for CVs longer than one page

\usepackage[T1]{fontenc}
\usepackage{charter}

% character encoding
\usepackage[utf8]{inputenc}                       % if you are not using xelatex ou lualatex, replace by the encoding you are using
\usepackage{CJKutf8}                              % if you need to use CJK to typeset your resume in Chinese, Japanese or Korean

% \usepackage[ulrcolor=cyan]{hyperref}

% \hypersetup{
%     colorlinks=true,
%     linkcolor=blue,
%     filecolor=magenta,      
%     urlcolor=cyan,
% }

% \urlstyle{same}


% adjust the page margins
% \usepackage[scale=0.75]{geometry}
\usepackage[scale=0.75, top=2.5em, right=5em, bottom=1em, left=5em]{geometry}

% personal data
\name{Hendry}{Khoza}
% \signature{Khoza SH}
\title{Software Engineer ERP AWS}                               % optional, remove / comment the line if not wanted
\address{26 Frangipani St}{Pretoria}% optional, remove / comment the line if not wanted; the "postcode city" and and "country" arguments can be omitted or provided empty
\phone[mobile]{+27 81-249-0306}                   % optional, remove / comment the line if not wanted
\email{h3khoza@gmail.com}                               % optional, remove / comment the line if not wanted
\homepage{www.hendry.xyz}                         % optional, remove / comment the line if not wanted

\begin{document}

\recipient{082 Vodacom Boulevard} {Midrand \\ 1685 \\ South Africa}
\date{\today}

\makeatletter
\renewcommand*{\makeletterclosing}{
  \@closing\\% <===================================================
  {\bfseries\@firstname~\@lastname}%
  \ifthenelse{\isundefined{\@enclosure}}{}{%
    \\%
    \vfil%
    {\color{color2}\itshape\enclname: \@enclosure}}%
    \vfil}
\makeatother


\opening{Dear Hiring team}

\closing{Yours sincerely,}
% \enclosure[Adjunto]{CV}          % use an optional argument to use a string other than "Enclosure", or redefine \enclname

\makelettertitle

This letter is to express my interest in the Software Engineering position with
Vodacom. With all my skills and experience, I know I will be a valuable member
of your team

I am a young, highly motivated Software Engineer based in the Gauteng province

with a strong ability to create highly-detailed, Quality software while being
consistent with engineering principles. I have studied Computer System
Engineering at the Tshwane University of Technology, and I have a strong
knowledge of what users enjoy when interacting with the software. In my years
of developing software, I have maintained a reputation for being extremely
efficient and professional. I am fluent in web development, notably NodeJS and
ReactJS. I have had experience in developing websites, web applications, mobile
applications. in addition to web development, I also have experience in cloud
computing as AWS

I am currently a freelancer, Developing software for clients. The number of
clients I receive keep growing, while the feedback I get is overwhelmingly
positive. I have developed an online store for a client who producer music to
sell beats. With beat store's target audience being young people, I developed
the website to be responsive, and accessible via mobiles phone. I am familiar
with making a tight deadline, because of this, my client appreciates working
with me.  In my free time, I enjoy building side project and learning a new
programming language

When I say I am a Software Engineer is more than a job title. What I do matters
I do not just write code, I build software that changes people's lives and that
is a huge responsibility. If you think for a minute about the peoples who use
the software I build... They put trust in me.
Quality of software is the heart of every line of code that I write. I always
write software that: 
\begin{itemize}
  \item works - The program does the task that is design to do
  \item can be modified - I make sure that my code is easy to read, understand or change
  \item reusable - I apply object-oriented design so that it will be easy to use part of the program to another program 
\end{itemize}

With Vodacom being one of the most exciting network companies in South Africa
right now, I have a strong desire to contribute my skills and more to ensure
that Vodacom is visually on top of its game. I am hungry for a challenge, and I
believe Vodacom is the perfect place for me to grow even more as a Software
Engineer and put my arsenal of skills to its proper use.

Thank you for considering me for the Software Engineer position within your
company. I look forward to meeting you. Please do not hesitate to contact me if
you have any questions.


\makeletterclosing

\end{document}

