%% start of file `template.tex'.
%% Copyright 2006-2013 Xavier Danaux (xdanaux@gmail.com).
%
% This work may be distributed and/or modified under the
% conditions of the LaTeX Project Public License version 1.3c,
% available at http://www.latex-project.org/lppl/.
%Version for spanish users, by dgarhdez

\documentclass[11pt,a4paper,roman]{moderncv}        % possible options include font size ('10pt', '11pt' and '12pt'), paper size ('a4paper', 'letterpaper', 'a5paper', 'legalpaper', 'executivepaper' and 'landscape') and font family ('sans' and 'roman')
% \usepackage[spanish,es-lcroman]{babel}


% moderncv themes
\moderncvstyle{classic}                            % style options are 'casual' (default), 'classic', 'oldstyle' and 'banking'
\moderncvcolor{green}                              % color options 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'
%\renewcommand{\familydefault}{\sfdefault}         % to set the default font; use '\sfdefault' for the default sans serif font, '\rmdefault' for the default roman one, or any tex font name
%\nopagenumbers{}                                  % uncomment to suppress automatic page numbering for CVs longer than one page

% character encoding
\usepackage[utf8]{inputenc}                       % if you are not using xelatex ou lualatex, replace by the encoding you are using
%\usepackage{CJKutf8}                              % if you need to use CJK to typeset your resume in Chinese, Japanese or Korean

% adjust the page margins
\usepackage[scale=0.75]{geometry}
%\setlength{\hintscolumnwidth}{3cm}                % if you want to change the width of the column with the dates
%\setlength{\makecvtitlenamewidth}{10cm}           % for the 'classic' style, if you want to force the width allocated to your name and avoid line breaks. be careful though, the length is normally calculated to avoid any overlap with your personal info; use this at your own typographical risks...

% personal data
\name{Hendry Khoza}
\title{Cover Letter}                               % optional, remove / comment the line if not wanted
\address{Dirección}{CP, Ciudad}{País}% optional, remove / comment the line if not wanted; the "postcode city" and and "country" arguments can be omitted or provided empty
\phone[mobile]{+27 81 249 0306}                   % optional, remove / comment the line if not wanted
%\phone[fixed]{+2~(345)~678~901}                    % optional, remove / comment the line if not wanted
%\phone[fax]{+3~(456)~789~012}                      % optional, remove / comment the line if not wanted
\email{h3khoza@gmail.com}                               % optional, remove / comment the line if not wanted
\date{\today}
%\homepage{www.johndoe.com}                         % optional, remove / comment the line if not wanted
%\extrainfo{additional information}                 % optional, remove / comment the line if not wanted
%\photo[64pt][0.4pt]{picture}                       % optional, remove / comment the line if not wanted; '64pt' is the height the picture must be resized to, 0.4pt is the thickness of the frame around it (put it to 0pt for no frame) and 'picture' is the name of the picture file
%\quote{Some quote}                                 % optional, remove / comment the line if not wanted

% to show numerical labels in the bibliography (default is to show no labels); only useful if you make citations in your resume
%\makeatletter
%\renewcommand*{\bibliographyitemlabel}{\@biblabel{\arabic{enumiv}}}
%\makeatother
%\renewcommand*{\bibliographyitemlabel}{[\arabic{enumiv}]}% CONSIDER REPLACING THE ABOVE BY THIS

% bibliography with mutiple entries
%\usepackage{multibib}
%\newcites{book,misc}{{Books},{Others}}
%----------------------------------------------------------------------------------
%            content
%----------------------------------------------------------------------------------
\begin{document}
%-----       letter       ---------------------------------------------------------
% recipient data
\recipient{Destinatario}{Departamento, Empresa}
\opening{Estimado Destinatario,}
\closing{Muchas gracias por su tiempo e interés y reciba un cordial saludo.}
\enclosure[Adjunto]{CV}          % use an optional argument to use a string other than "Enclosure", or redefine \enclname
\makelettertitle

My name is Hendry and I'm currently doing my final year in computer engineering at Tshwane University of Technology(TUT). I'm so excited to apply for the Vodacom Discover Graduate program.

I've been using Vodacom ever since my first phone and I really enjoy how reliable it is even in rural areas. My favorite service from Vodacom was Vodacom Millionaires. I used to play it every week,  every Vodacom customer used to get two free entries to play.  I've won airtime multiple times from Vodacom Millionaire.

I believe I'd be a great fit for the internship role because of the following reasons:

\begin{itemize} \itemsep1em 
	\item Any first-year student in Computer Engineering at TUT is required to complete 14 modules ( 7 per semester). Although it wasn't easy, I had to manage my time to be more flexible and be dedicated to my school work. That paid off, I managed to pass all the modules with an average mark of 70%.
  
	\item Due to my good pass rate mark, I was offered a position to be a Student Assistant for Technical Programming and Engineering Mathematics. One of my responsibilities as a student Assistant was to explain certain topics to students that have difficulties understanding during lecture time. This improves my communication skills and public speaking. It also helped me understand the content more because I couldn't just study to forget I had to explain what I studied in simple terms that anyone can understand.

	\item I remember when I wrote my first Hello world program It felt like I was part of the minority of people who can code in this world. My goal as a programmer was to create games. I've never got to reach my goal but trying to pursue this goal created a passion in me about writing computer programs. I've contributed to open-source projects and built my own portfolio website.

	\item Since high school, I managed to pass complicated subjects with flying colors, such as Maths, Physics, and Life Science. This carry-on even at university from Technical Programming to Engineering Mathematics. The most challenging Module was Maths 3.

	\item While I'm here at university, I make extra income by developing websites for clients. Most of my customers are small business owners who want to have their first website. A recent website that I   develop is reserved (link). Developing something that you want is much easier than developing something that a customer wants. I even spent less time developing websites and more time writing reports and Sending invoices. I'm happy about what I'm doing, it teaches me a lot to be customer-obsessed.

\end{itemize}



\vspace{0.5cm}


\makeletterclosing

\end{document}


%% end of file `template.tex'.
